Learning and comparing functional connectomes across subjects

### 2013-02-24 paper.tex
Forgotten acknowledgment

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

@@

GV acknowledges funding from the NiConnect grant, as well as many
insightful discussions with Andreas Kleinschmidt on on-going activity and
Bertrand Thirion on statistical data processing.

>>>>

% For review: line numbers
\usepackage[pagewise]{lineno}

@@

% Modification tracking
\usepackage{xcolor}
\usepackage[normalem]{ulem}
\newcommand{\ADDED}[1]{\textcolor{blue}{\uline{#1}}}
\newcommand{\DELETED}[1]{\textcolor{red}{\sout{#1}}}

% Show the old version
%\renewcommand{\ADDED}[1]{}
%\renewcommand{\DELETED}[1]{#1}

% Show the new version
%\renewcommand{\ADDED}[1]{#1}
%\renewcommand{\DELETED}[1]{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
% Show line numbers
\linenumbers
\linenumbersep 3pt\relax
\renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{black!50}}

@@

GV acknowledges funding from the NiConnect grant and the Dynamic
Diaschisis project DEQ20100318254 from \emph{Fondation pour la Recherche
M\'edicale}, as well as many insightful discussions with Andreas
Kleinschmidt on on-going activity and Bertrand Thirion on statistical
data processing.
